Modelling the Trojan Asteroids

### 2020-04-24 Report/draft1.tex
perturbation_3D written (not tidy) pre-clean up planetary_mass variation

To consider a varying planet mass, it was considered preferable to avoid reconstructing all functions to take this as an argument as this requires re-evaluating all initial derived constants. Therefore, I iterate over alternative masses, re-defining constant values in this instance, and then directly import the required functions to compute the orbit. \textbf{REPHRASE?}

@@

\subsection{Perturbations in Z-direction} \label{3D}
Perturbations in the Z-direction are aligned with angular velocity vector for rotating frame, so experience no virtual forces in this direction, and oscillate under the influence of gravity alone. Considering small perturbations in the z direction (so that the distance from the CoM can be considered constant), the period of such oscillations tends to the orbital period of the rotating frame, under Newtonian gravity.

These are measured to be $11.85 \pm 0.48$ years, in strong agreement with the theoretical predictions.

@@

\textit{Wander from unperturbed initial conditions is calculated within "\textit{lagrange\_stability}", with ODE solver performance also evaluated here.
Orbits in the stationary frame are animated and saved within "\textit{stat\_frame\_video}".

2D perturbations are characterised in \textit{perturbation\_2D}, while perturbations in the z direction are considered in \textit{perturbation\_3D}. Variation in planetary mass, for results in section \ref{planet}, are given in \textit{planet\_mass\_variation}.}

>>>>

To consider a varying planet mass, it was considered preferable to avoid reconstructing all functions to take this as an argument, as this requires re-evaluating all initial derived constants. Therefore, I iterate over alternative planetary masses, re-defining constant values in this instance, and then directly importing the required functions to compute the orbit. \textbf{REPHRASE?}

@@

\subsection{Perturbations in Z-direction} \label{3D}
Perturbations in the Z-direction are aligned with angular velocity vector for rotating frame, so experience no virtual forces in this direction, and oscillate under the influence of gravity alone. Considering small perturbations in the z direction (so that the distance from the CoM can be considered constant), the period of such oscillations tends to the orbital period of the rotating frame, under Newtonian gravity. These are measured to be $11.85 \pm 0.48$ years, in strong agreement with the theoretical predictions.

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{Figures/z_perturbations5c}
	\caption{Variation of wander with increasing z perturbations. A strong linear component is observed initially in the un-perturbed case, however tends towards the perturbed quadratic case, while the linear offsets result from the initial perturbation in the xy plane.}
	\label{fig:zwander}
\end{figure}

The overall wander, however, is observed to follow Fig \ref{fig:zwander}.
It is suggested that, while the maximum deviation from the Lagrange point in the z direction is simply twice the initial perturbation, wander in the xy plane increases quadratically. This can be initiated from a radial displacement due to the reduced gravitational force  under the z perturbation, demonstrated in Fig \ref{fig:zorbit}, or more significantly from an initial perturbation in the xy plane.

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{Figures/z_perturb_orbit}
	\caption{Orbit of Greek asteroids following a 0.2 AU perturbation in the positive z direction, over 12 orbital periods. Note the initial outwards radial displacement despite the lack of perturbation in the xy plane, and subsequent tadpole-like orbit.}
	\label{fig:zorbit}
\end{figure}

@@

Wander from unperturbed initial conditions is calculated within "\textit{lagrange\_stability}", with ODE solver performance also evaluated here.
Orbits in the stationary frame are animated and saved within "\textit{stat\_frame\_video}".

2D perturbations are characterised in \textit{perturbation\_2D}, while perturbations in the z direction are considered in \textit{perturbation\_3D}. Variation in planetary mass, for results in section \ref{planet}, are given in \textit{planet\_mass\_variation}.
